Implicit assumptions and their impact on photometric redshift PDF performance in the context of LSST

### 2018-11-29 paper/tex/discussion.tex

\section{Discussion}
\label{sec:discussion}
%(Sam Schmidt, Ofer Lahav, Jeff Newman, Alex Malz, Eve Kovacs, Tony Tyson, Tina Peters)
In this paper we presented results evaluating the computation of individual galaxy photometric redshift PDFs for twelve photo-$z$ codes.  As discussed in Section~\ref{sec:metrics} each $p(z)$ should accurately reflect the relative likelihood as a function of redshift for each galaxy in an informative way; that is, the estimates should provide useful information per individual galaxy, not just the ensemble.  All codes were provided a set of representative training data and tested on an idealized set of model galaxies with high signal-to-noise and photometry with no confounding effects due to blending, instrumental effects, the night sky, or other complications included.  The goal was not to determine a ``best'' photo-$z$ code: in many ways, this was a baseline test of a ``best case scenario'' to predict the expected photo-$z$ performance if a stage IV dark energy survey was to obtain complete training samples and perfectly calibrated their multi-band photometry.  Given these idealized conditions, any deficiencies observed in a photo-$z$ code's performance should be a cause for concern, and may be evidence of a problem with either/both of the specific code implementation or the underlying algorithm.  In order to meet the stringent LSST goals for photo-$z$ performance, identifying and correcting such problems is an important first step before tackling more realistic data in future challenges, and codes that do not perform well may not be worth pursuing in future challenges.  Many of the codes tested performed well; however, several did not meet the stringent goals that have been laid out for LSST photometric redshift performance for individual galaxies, as laid out in the LSST SRD (See Section~\ref{sec:intro}.  This is a cause for concern, given the idealized conditions, and the individual code responses will be studied in detail moving forward.  If methods can not reach the goals on idealized data, then they will almost surely not meet those same goals when the more complex problems that we expect to arise from real LSST data are included.  The results presented in this paper enable an evaluation of which algorithms are the most promising moving forward, and potentially point to implementation choices or mistakes which could be improved or corrected in others.

@@

In future papers a focus of the {\it LSST Dark Energy Science Collaboration Photo-z Working Group} will be to add more and more complexity to our simulated data in order to test photo-$z$ algorithms in increasingly realistic conditions.  The most pressing concern is the impact of incomplete spectroscopic training samples.  The SEDs for the galaxy sample in this paper were constructed form linear combinations of five basis SED templates.  Future simulations will also include more complex SED information, with a more realistic range of physical properties, and the inclusion of AGN effects.  As discussed extensively in \citet{Newman:2015} a representative set of spectroscopically confirmed galaxies spanning the full range of both redshift and apparent magnitude is necessary as a training set to characterize the mapping from broad-band fluxes to photometric redshifts.
%However, due to a combination of factors due to both the galaxy SEDs and limitations of spectrographic instruments, redshift samples are known to be systematically incomplete, where certain galaxy types and redshift intervals fail to yield a redshift even at the longest integration times on current and near-future instruments.  The more representative the training data, the better the performance of photo-$z$ algorithms will be.
Current and upcoming surveys are putting significant effort into obtaining these training samples \citep[e.~g.\,][]{Masters:2017}, however we still expect significant incompleteness for LSST-like samples, particularly at faint magnitudes.  We plan to produce a realistically incomplete training set of spectroscopic galaxies, modeling the performance of spectrographs, emission-line properties, and expected signal-to-noise to determine which galaxies will fail to yield a secure redshift.  In addition to outright redshift failures we will model the inclusion of a small number of falsely identified secure redshifts where misidentified emission lines or noise spikes cause an incorrect redshift solution to be marked as a high quality identification.  Even sub-per cent level contamination by false redshifts can impact photo-$z$ solutions at levels comparable to the stringent  requirements of some LSST science cases.
We expect different systematics to occur in different photo-$z$ codes in response to training on incomplete data, particularly some of the machine learning methods.  The response of the codes will inform future directions of code development.

>>>>

\section{Discussion and Future Work}
\label{sec:discussion}
%(Sam Schmidt, Ofer Lahav, Jeff Newman, Alex Malz, Eve Kovacs, Tony Tyson, Tina Peters)
In this paper we presented results evaluating the computation of individual galaxy photometric redshift PDFs for twelve photo-$z$ codes.  As discussed in Section~\ref{sec:metrics} each $p(z)$ should accurately reflect the relative likelihood as a function of redshift for each galaxy in an informative way; that is, the estimates should provide useful information per individual galaxy, not just the ensemble.  All codes were provided a set of representative training data and tested on an idealized set of model galaxies with high signal-to-noise and photometry with no confounding effects due to blending, instrumental effects, the night sky, or other complications included.  The goal was not to determine a ``best'' photo-$z$ code: in many ways, this was a baseline test of a ``best case scenario'' to predict the expected photo-$z$ performance if a stage IV dark energy survey was to obtain complete training samples and perfectly calibrated their multi-band photometry.  Given these idealized conditions, any deficiencies observed in a photo-$z$ code's performance should be a cause for concern, and may be evidence of a problem with either/both of the specific code implementation or the underlying algorithm.  In order to meet the stringent LSST goals for photo-$z$ performance, identifying and correcting such problems is an important first step before tackling more realistic data in future challenges, and codes that do not perform well may not be worth pursuing in future challenges.  Many of the codes tested performed well; however, several did not meet the stringent goals that have been laid out for LSST photometric redshift performance for individual galaxies, as laid out in the LSST SRD (See Section~\ref{sec:intro}.  This is a cause for concern, given the idealized conditions, and the individual code responses will be studied in detail moving forward.  If methods can not reach the goals on idealized data, then they will almost surely not meet those same goals when the more complex problems that we expect to arise from real LSST data are included.  The results presented in this paper enable an evaluation of which algorithms are the most promising moving forward, and potentially point to implementation choices or mistakes which could be improved or corrected in others.

@@

In future papers a focus of the {\it LSST Dark Energy Science Collaboration Photo-z Working Group} will be to add more and more complexity to our simulated data in order to test photo-$z$ algorithms in increasingly realistic conditions.  The most pressing concern is the impact of incomplete spectroscopic training samples.  The SEDs for the galaxy sample in this paper were constructed form linear combinations of five basis SED templates.  Future simulations will also include more complex SED information, with a more realistic range of physical properties, and the inclusion of AGN effects, a more insidious problem, where AGN features may not be apparent, but the colors and other host galaxy properties are perturbed relative to galaxies with an inactive nucleus.  In such cases, the presence of the AGN may induce a bias if the template SEDs or empirical datasets do not include low-level AGN counterparts.

As discussed extensively in \citet{Newman:2015} a representative set of spectroscopically confirmed galaxies spanning the full range of both redshift and apparent magnitude is necessary as a training set to characterize the mapping from broad-band fluxes to photometric redshifts.
%However, due to a combination of factors due to both the galaxy SEDs and limitations of spectrographic instruments, redshift samples are known to be systematically incomplete, where certain galaxy types and redshift intervals fail to yield a redshift even at the longest integration times on current and near-future instruments.  The more representative the training data, the better the performance of photo-$z$ algorithms will be.
Current and upcoming surveys are putting significant effort into obtaining these training samples \citep[e.~g.\,][]{Masters:2017}, however we still expect significant incompleteness for LSST-like samples, particularly at faint magnitudes.  We plan to produce a realistically incomplete training set of spectroscopic galaxies, modeling the performance of spectrographs, emission-line properties, and expected signal-to-noise to determine which galaxies will fail to yield a secure redshift.  In addition to outright redshift failures we will model the inclusion of a small number of falsely identified secure redshifts where misidentified emission lines or noise spikes cause an incorrect redshift solution to be marked as a high quality identification.  Even sub-per cent level contamination by false redshifts can impact photo-$z$ solutions at levels comparable to the stringent  requirements of some LSST science cases.
We expect different systematics to occur in different photo-$z$ codes in response to training on incomplete data, particularly some of the machine learning methods.  The response of the codes will inform future directions of code development.
